##Summary of Amalga Data Pull for Treatment Cohort
####*Nabiha Huq Saifee*
####*November 22, 2014*

Sally Lee from the Biomedical Informatics group pulled data for **`r nrow(Tdemog)` patients** in the treatment group based on MRNs and procedure dates I obtained from PSBC charts. 

The age range of these patients is from **`r min(Tdemog$AdmissionAge)` to `r max(Tdemog$AdmissionAge)` years of age** with **mean age of `r round(mean(Tdemog$AdmissionAge),1)` (SD `r round(sd(Tdemog$AdmissionAge),1)`)** and **median age of `r median(Tdemog$AdmissionAge)`.**  A plot of the distribution of ages is shown below.  
```{r echo=FALSE}
plot(table(Tdemog$AdmissionAge), main="Age Distribution of NSTI group receiving Therapeutic Plasma Exchange", xlab = "Admission Age", ylab = "Number of Patients")
```

The treatment cohort contains predominantly males.
```{r echo=FALSE} 
Tdemog$Sex[Tdemog$Sex %in% c("Male","M")] <- "Male" 
Tdemog$Sex[Tdemog$Sex %in% c("Female","F")] <- "Female"
Number<-table(Tdemog$Sex)
Percentage<-round(prop.table(table(Tdemog$Sex))*100,1)
rbind(Percentage,Number)
```

The distribution of race in the table looks as follows:
```{r echo=FALSE}
#RaceNumber<-table(Tdemog$RaceDescr)
RacePercentage<-round(prop.table(table(Tdemog$RaceDescr))*100,1)
RacePercentage
#rbind(RacePercentage,RaceNumber)
```





